The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation rate

### 2022-08-14 src/tex/ms.tex
worked through selmas comments

% Title
\title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate  }

@@

@@

\author[0000-0002-8901-6994]{Martyna Chru{\'s}li{\'n}ska}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}

\author{et al?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract with filler text
\begin{abstract}
New observational facilities are probing astrophysical transients such as gravitational wave (GW) sources at ever increasing redshifts. To interpret these observation we need to compare them to predictions from stellar population models. These models are very sensitive to the metallicity-dependent star formation rate density (\SFRDzZ). 
% Large uncertainties remain in the value and shape of the \SFRDzZ, especially at the low metallicities that are crucial to the formation of GW events.
Understanding the behaviour of the adopted \SFRDzZ is essential to explain simulation results. 
%
% Various approaches to approximate \SFRDzZ exist, ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
In this work, we propose a simple analytical form for \SFRDzZ. 
The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
Variations of this analytical form can be easily interpreted, because the parameters are intuitively linked to the shape of \SFRDzZ. %Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
%
We fit our analytical form to the star-forming gas of the cosmological TNG100 simulations and find that it is able to capture the main behaviour well. 
%
As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH). Our main findings are I) the low mass end is least affected by variations in \SFRDzZ, II) the distribution of metallicities at low redshift affects the normalisation of of the BBH merger rate, while III) the redshift evolution of the metallicity distribution affects the high-mass slope of the mass distribution and IV) the shape of the overall star-formation rate has a small impact on the local mass distribution.
\end{abstract}

% Interpreting these observations requires comparison to predictions from stellar population models. However, the model predictions  are very sensitive to the adopted assumptions about the metallicity-dependent star formation rate density. Hence in order to 
% Comparing these observations to predictions from stellar population models requires assumptions about the metallicity-dependent star formation rate density. Various approaches exist 
% ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations. Both these approaches come with advantages and disadvantages and inherent uncertainties.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction \label{sec: intro}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe. Transient phenomena, including core collapse supernovae, (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events are especially sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe.
Gravitational astronomy in particular has seen explosive growth in the number of detections in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}. In order to correctly model and interpret these observations, it is fundamental to know the rate of star formation at different metallicities throughout cosmic history, i.e. the metallicity-dependent star formation rate density \SFRDzZ \citep[see also the recent review by][]{chruslinska2022_review}.

It is difficult to observationally constrain the shape of \SFRDzZ (see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats). Even at low redshifts, the low metallicity part of the distribution is poorly constrained \citep{Chruslinska+2021}.
Nonetheless, several methods exist to estimate the metallicity dependent star-formation rate. The first method combines a mass-metallicity relation (MZ-relation) and a galaxy stellar mass function (GSMF) \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
Another way is to directly extract the metallicity density fraction from cosmological simulations \citep[e.g.]{Mapelli2017, Briel+2021}.
Alternatively, one can combine an observed star formation rate, \SFRDz, like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with some belief about the shape of the metallicity density distribution, such as was was done in \cite{Neijssel+2019}.

%Arguments: cosmological simulations work at high z,  but are they real? observations 
In this work we follow the latter approach and propose a flexible analytical model for the \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available. The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
The purpose of this model is to allow for an intuitive interpretation of the effects of the \SFRDzZ on the inferred rates of astrophysical transients. By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored.% through varying the parameters that control its shape.

@@

% %
% The task we have at hand here is not a standard textbook fitting problem given the specific aims and requirements that we have that are driven by the astrophysical applications we have in mind. Qualitatively, our aims are the following. Our main aim is to find solution for the free parameters, for which the expression reproduces the overall behaviour that is observed in the cosmological simulations. For the purposes we have in mind, it will be more important to prioritise fitting the large scale trends, while we are not so interested in smaller scale fluctuations. We further prioritise getting the bulk of the cosmic star formation right and are less interested in capturing the behaviour in metallicity and redshift bins where the cosmic star formation rate is very low and thus insignificant for the overall picture. Finally, we are especially interested in capturing the asymmetry of the metallicity distribution. 
% There is not one unique procedure that will full fill these criteria.  After experimenting with different criteria we have adopted the procedure below, which we believe works well for the aims we have in mind.  
%%
% Large uncertainties exist in the shape and redshift evolution of both \SFRDz, and the cosmic distribution of metallicities \dpdZ (see e.g. \citealt{Chruslinska2019_obs}, \citealt{Boco2021} and \citealt{Chruslinska+2021} for an extended discussion on the metallicity dependent star formation rate density, in light of empirical data).

% To construct \SFRDzZ from empirical data, one can estimate \dpdZ by combining observed mass-metallicity relations with galaxy stellar mass functions \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_obs, Broekgaarden+2021b}. Alternatively, one could extract \SFRDzZ directly from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}. 
% \citet{Mapelli2017} and \cite{Briel+2021}  but instead of directly extracting the \SFRDzZ from a cosmological simulation 
% we take an approach similar to \cite{LangerNorman}, but instead of following the observed mean metallicity with redshift, we fit our combined analytical representations of \SFRDz and \dpdZ to simulation data.

@@

\begin{equation}
\label{eq: total sfrd}
\boxed{
        \SFRDzZ = \SFRDz \times \dPdZ.
        }
\end{equation}
The first term is the star formation rate density, \SFRDz, that is the amount of mass formed in stars per unit time and per unit comoving volume at each redshift. The second term, \dpdZ, is a probability density function that expresses what fraction of star formation occurs at which metallicity, at each redshift.

@@

% $a=0.02$, $b=1.48$, $c=4.45$ and $d=5.9$ as best fitting parameters,
\subsection{The metallicity probability density function}
For the probability distribution of metallicities we draw inspiration from the approach by \citep[e.g.\ ][]{Neijssel+2019} who used a log-normal distribution. Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail towards low metallicity combined with a very limited tail towards higher metallicity, when plotted as a function of $\log_{10} Z$. To capture this behavior we adopt a skewed-log-normal distribution instead. This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep[first introduced by][]{Ohagan+1976}. %for a more clear derivation
%This allows us to more accurately capture the asymmetry in the metallicity distribution at each redshift.

The skewed-log-normal distribution of metallicities is defined as:
% See eq. 1 here: https://www.emis.de/journals/RCE/V36/v36n1a03.pdf
\begin{equation}
\begin{aligned}
\label{eq: pure log skew}
\mathrm{\frac{dP}{dZ}}(Z) &= \frac{1}{Z} \times \frac{\rm dP}{{\rm d}\ln Z}  \\
&= \frac{1}{Z} \times \frac{2}{\omega}
    \underbrace { \phi \left(\frac{\ln Z - \xi}{\omega}\right)
                 }_{(1)}
    \underbrace {
                \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right)
                }_{(2)},
\end{aligned}
\end{equation}

\noindent where (1) is the standard log-normal distribution, $\phi$,
%
\begin{equation}
\label{eq: log normal and CDF}
 \phi \left(\frac{\ln Z - \xi}{\omega}\right) \equiv 
% \underbrace{
    \frac{1}{\sqrt{2 \pi}} 
    \exp{
         \left\{
            -\frac{1}{2} \left(\frac{\ln Z - \xi}{\omega}\right)^2
        \right\}
        }
  %  }_{(1)} 
    \end{equation}
and (2) is the new term that allows for asymmetry, which is equal to the cumulative of the log-normal distribution, $\Phi$,
    \begin{equation}
    \begin{array}{cc}
 \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right) &\equiv 
% \underbrace {
    \frac{1}{2} 
    \left[ 
        1 + {\rm erf}
            \left\{
%                \frac{ \left(\alpha \frac{\ln(Z) - \xi}{\omega} \right)  }{\sqrt{2}} 
                \alpha \frac{\ln Z - \xi}{\omega \sqrt{2}}
            \right\} 
    \right] \\
    %}_{(2)}.
%   &=    %%% I dont think this belongs here: \frac{1}{2} 
%       \int_{\infty}^{\alpha\left( \frac{\ln Z -\xi}{\omega}\right)}
%       \frac{1}{\sqrt{2\pi}}e^{-t^2/2}dt
    \end{array}
\end{equation}

%
\noindent This introduces three parameters, $\alpha, \omega$ and $\xi$ each of which may depend on redshift. The first parameter, $\alpha$, is known as the ``shape''. It affects the skewness of the distribution and thus allows for asymmetries between metallicities that are higher and lower than the mean.  The symmetric log-normal distribution is recovered for $\alpha=0$. The second parameter, $\omega$  is known as the ``scale''. It provides a measure of the spread in metallicities at each redshift.   Finally, $\xi$, is known as the ``location'', because this parameter plays a role in setting the mean of the distribution at each redshift.

@@

We will also allow the ``scale'' $\omega$ to evolve with redshift in a similar manner, 
\begin{equation}
\label{eq: sigma z}
    \omega(z) = \omega_0 \cdot 10^{\omega_z \cdot z}.
\end{equation}
where $\omega_0$ is
%$\omega_0 = 1.125$, 
the width of the metallicity distribution at $z=0$, and $\omega_z$
%$\omega_z = 0.048$, 
the redshift evolution of the scale.

@@

\paragraph{Asymmetry of the metallicity distribution: $\alpha$}
We have considered variations where the ``skewness'' $\alpha$ varies with redshift but we did not find very significant improvements compared to the simpler assumption where $\alpha$ is kept constant.

%We allow the mean metallicity and the spread of metallicities to evolve with redshift by allowing the ``location'' $\xi(z)$ and ``scale'' $\omega(z)$ to vary as functions of redshift. We have also considered to allow the ``skewness'' to vary with redshift, but we did not find a very significant improvement and we opted to keep this constant.

@@

\noindent where $\xi(z)$ and $\omega(z)$ are defined in Equations~\ref{eq mu z} and \ref{eq: sigma z} respectively and we have assumed $\alpha$ to be constant.

%, and our fit value for $\alpha = -1.77$. Our set of parameters for \dpdZ is thus:  $\mu_0 = 0.025, \mu_z = -0.048, \sigma_0 = 1.125, \sigma_z = 0.048$ and $\alpha = -1.77$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Illustris-TNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The IllustrisTNG-project \citep[or TNG in short][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018} considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations. In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.
Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.

The models implemented in the publicly available TNG simulations\footnote{ \url{https://www.tng-project.org/}} have lead to many successes. For a more extended discussion focused on the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}. In short, star formation in the TNG simulations is calibrated against the Kennicutt–Schmidt relation \citep[][]{Schmidt1959,Kennicutt1989}. The stellar metallicity yields are and updated version of the original Illustris simulations as described in \cite{Pillepich2018}. Star particles deposit metals into the gas through Type Ia and Type II supernovae, as well as through Asymptotic Giant Branch mass loss. 
% Positives on TNG
The TNG simulations have been shown to match observational constraints on the mass-metallicity relation of galaxies up to $z = 2$ \citep{Torrey+2019}, as well as iron abundances \citep{FirstResTNG_Naiman2018} and the metallicity gradients within galaxies at low redshift \citep{Hemler+2021}. %They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018}   
Several studies have already used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2021,Bavera+2022}. In particular, \cite{Briel+2021} show that the \SFRDzZ from the TNG and the EAGLE \citep{Schaye+2015,Crain+2015} simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.

% Downsides of TNG100 
On the other hand, large uncertainties and crude approximations remain in all contemporary cosmological simulations, thus also in the TNG simulations. For example, dust is not included in the TNG simulations, which could mean that metallicity of the star-forming gas is overestimated. Furthermore, all mass loss from massive stellar winds \citep[e.g.][]{Dray+2003}, pair-pulsational supernovae \citep[e.g.][]{Renzo+2020} binary interactions \citep[e.g.][]{Farmer2021_carbonfootprint} and their ionising effects \citep[][]{Gotberg+2020,DoughtyFinlator2021} are ignored.  Moreover, the uniform ionising UV background is turned on abruptly at $z=6$, which crucially impacts the amount of low metallicity star formation at low redshift.

These large uncertainties call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work. Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated data or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here \todo{add link}}.

@@

\begin{deluxetable}{clc | cc}
\label{tab: fit params}
\tablecaption{Best fitting parameters for our \SFRDzZ fit to TNG100 data.}
\tablehead{\colhead{dP/dZ } & \colhead{description} & \colhead{best fit} & \colhead{SFRD(z)} & \colhead{best fit} } 
\startdata
$\mu_0$    & mean metallicity $z=0$     & 0.025 &  $a$ &  0.02 \\
$\mu_z$    & mean metallicity $z$ evol. & -0.048 &  $b$ &  1.48 \\
$\alpha$   & shape (skewness)           & -1.767 &  $c$ &  4.45 \\
$\omega_0$ & scale $z=0$                & 1.125 &  $d$ &  5.90 \\
$\omega_z$ & scale $z$ evol.            & 0.048 &   \\
\enddata
\end{deluxetable}

@@

Adopting a skewed-lognormal metallicity distribution allows for a tail of low metallicity star formation out to low redshifts. To emphasise the difference between a skewed-lognormal and a symmetric lognormal distribution, we show the phenomenological model from \cite{Neijssel+2019} in dotted grey. Their model falls within the family of functions that is encompassed by our model described in Section \ref{sec: model for sfrd(zZ)}. \footnote{The phenomenological model from \cite{Neijssel+2019} is recovered by adopting $\mu_0= 0.035$, $\mu_z=-0.23$, $\omega_0=0.39 $, $\omega_z = 0$, $\alpha = 0$, $a=0.01$, $b=2.77$, $c=2.9$ and $d=4.7$. }
% The \SFRDzZ from \cite{Neijssel+2019} was optimised to match the local rate of double compact object mergers as presented in the second gravitational-wave catalogue. However, the resulting symmetric distribution cuts-off virtually all low-metallicity ($Z\leq 10^{-2.5}$) star formation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\script{SFR_z.py}
\includegraphics[width=0.47\textwidth]{figures/SFR_redshift.pdf}
\caption{Comparison of different \SFRDz
 \label{fig: SFR(z)}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

% Title
% \title{ A flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate  }
% \title{ A flexible expression for the metallicity-dependent cosmic star formation rate: }
\title{The location of features in the mass distribution of merging binary black holes does not depend on the metallicity-dependent cosmic star formation rate}

@@

\author[0000-0002-8901-6994]{M. Chru{\'s}li{\'n}ska}
\affiliation{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85748 Garching, Germany}

\author[0000-0002-8901-6994]{L. Hernquist}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract with filler text
\begin{abstract}
New observational facilities are probing astrophysical transients such as stellar explosions and gravitational wave (GW) sources at ever increasing redshifts. To interpret these observation we need to compare them to predictions from stellar population models. These models, require the metallicity-dependent star formation rate density (\SFRDzZ) as an input. Large uncertainties remain in the shape and evolution of this function, and understanding its behaviour is essential to explain simulation results. 
% Large uncertainties remain in the value and shape of the \SFRDzZ, especially at the low metallicities that are crucial to the formation of GW events.
% Understanding the behaviour of the adopted metallicity distribution with which stars form is essential to explain simulation results. 
% Various approaches to approximate \SFRDzZ exist, ranging from fully empirical prescriptions to prescriptions that are based on cosmological simulations.
In this work, we propose a simple analytical function for \SFRDzZ. 
% The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift. 
Variations of this function can be easily interpreted, because the parameters link to its shape in an intuitive way. %Our hope is that this expression provides a useful starting point for making predictions and comparison with observations.
We fit our analytical function to the star-forming gas of the cosmological TNG100 simulations and find that it is able to capture the main behaviour well. 
%
As an example application, we investigate the effect of systematic variations in the \SFRDzZ parameters on the predicted mass distribution of locally merging binary black holes (BBH). Our main findings are I) the location of features is remarkably robust against variations in the metallicity-dependent star formation rate and II) the low mass end is least affected by these variations. This is promising as it increases our chances to constrain the physics that governs the formation of these objects.
We further find that III) the skewness, mean, and width of the metallicity distribution at low redshift affect the overall rate, while IV) the redshift evolution of the width and the mean of the metallicity distribution affects the slope at the high-mass end of the distribution. 
% IV) the shape of the overall star-formation rate has a small impact on the local mass distribution.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction \label{sec: intro}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A myriad of astrophysical phenomena depend critically on the rate of star formation throughout the cosmic history of the Universe. Exotic transient phenomena, including (pulsational) pair-instability supernovae, long gamma-ray bursts and gravitational wave (GW) events appear to be especially sensitive to the metallicity at which star formation occurs at different epochs throughout the Universe \citep[e.g.,][]{Langer+2007,Fruchter+2006,LIGO2016_implications}.
Gravitational astronomy in particular has seen explosive growth in the number of detections in the past decade \citep[][]{GWTC1,GWTC2,GWTC3}. In order to correctly model and interpret these observations, it is fundamental to know the rate of star formation at different metallicities throughout cosmic history, i.e. the metallicity-dependent star formation rate density  \citep[\SFRDzZ, see also the recent review by][]{chruslinska2022_review}. Throughout this work little $z$ refers to the redshift and $Z$ the metallicity of star formation.

It is difficult to observationally constrain the shape of \SFRDzZ, see \cite{Chruslinska2019_obs} for an extensive overview and discussion of relevant observational caveats. Even at low redshifts, the low metallicity part of the distribution is poorly constrained \citep{Chruslinska+2021}.
Nonetheless, several methods exist to estimate the metallicity dependent star-formation rate. The first method combines a galaxy mass-metallicity relation, MZ-relation and a galaxy stellar mass function, GSMF \citep[see e.g.][]{Dominik+2013}.
% \citep[see e.g.][]{Chruslinska+2018, Chruslinska2019_effectCO, Broekgaarden+2021a}.
On can also directly extract the metallicity density fraction from cosmological simulations \citep[e.g.][]{Mapelli2017, Briel+2021}.
Alternatively, one can combine an observed star formation rate, \SFRDz, like from \cite{MadauDickinson2014} or \cite{Madau+2017}, and convolve this with an assumed function for the shape of the shape of the metallicity density distribution, such as was was done in \cite{LangerNorman, Neijssel+2019}.

%Arguments: cosmological simulations work at high z,  but are they real? observations 
In this work we follow the latter approach and propose a flexible analytical model for the \SFRDzZ that can be fit to the output of both cosmological simulations, and observational data constraints where available. 
In contrast to earlier work  \citep{LangerNorman, Neijssel+2019}, we adopt a skewed-lognormal distribution of metallicities that can capture the asymmetry in the low and high metallicity tails. %to capture the tail of low metallicity star formation at low redshift. 
% The novelty of this model lies in a skewed-lognormal distribution of metallicities, that captures the tail of low metallicity star formation at low redshift.

The purpose of this proposed form is twofold.  
First of all, the form we propose allows for an intuitive interpretation of the free parameters. This allows us to get better insight of the impact of changes in these parameters on the inferred ranges of astrophysical transients (as we demonstrate in this work using GW predictions as an example). By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored.
Secondly, we hope that this form will facilitate a more sensible way for useful inference on large (future) datasets of astrophysical transients, such as the ever growing catalogue of gravitational wave transients. Our hope is that the constraints on the free parameters in the analytical form we propose, can provide a more useful guidance when comparing with the outcome of the predictions of cosmological simulations. 
% is to allow for an intuitive interpretation of the effects of the \SFRDzZ on the inferred rates of astrophysical transients. By adopting an analytical, parametrized form for \SFRDzZ, the large uncertainties in \SFRDzZ can be systematically explored.% through varying the parameters that control its shape.

@@

@@

\begin{equation}
\label{eq: total sfrd}
\boxed{
        \SFRDzZ = \SFRDz \times \dPdZ.
        }
\end{equation}
The first term is the star formation rate density, \SFRDz, that is the amount of mass formed in stars per unit time and per unit comoving volume at each redshift, $z$. The second term, \dpdZ, is a probability density function that expresses what fraction of star formation occurs at which metallicity, $Z$, at each redshift.

@@

% $a=0.02$, $b=1.48$, $c=4.45$ and $d=5.9$ as best fitting parameters,
\subsection{The metallicity probability density function}
For the probability distribution of metallicities we draw inspiration from the approach by \citep[e.g.\ ][]{Neijssel+2019} who used a log-normal distribution. Unfortunately, this expression does not capture the asymmetry well that we see in the results of the cosmological simulations, which show an extended tail in  $\log_{10} Z$ towards low metallicity combined with a very limited tail towards higher metallicity. To capture this behaviour we adopt a skewed-log-normal distribution instead. This is an extension of the normal distribution that introduces an additional shape parameter, $\alpha$, that regulates the skewness \citep[first introduced by][]{Ohagan+1976}.

The skewed-log-normal distribution of metallicities is defined as:
% See eq. 1 here: https://www.emis.de/journals/RCE/V36/v36n1a03.pdf
\begin{equation}
\begin{aligned}
\label{eq: pure log skew}
\mathrm{\frac{dP}{dZ}}(Z) &= \frac{1}{Z} \times \frac{\rm dP}{{\rm d}\ln Z}  \\
&= \frac{1}{Z} \times \frac{2}{\omega}
    \underbrace { \phi \left(\frac{\ln Z - \xi}{\omega}\right)
                 }_{(a)}
    \underbrace {
                \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right)
                }_{(b)},
\end{aligned}
\end{equation}

\noindent where (a) is the standard log-normal distribution, $\phi$,
%
\begin{equation}
\label{eq: log normal and CDF}
 \phi \left(\frac{\ln Z - \xi}{\omega}\right) \equiv 
% \underbrace{
    \frac{1}{\sqrt{2 \pi}} 
    \exp{
         \left\{
            -\frac{1}{2} \left(\frac{\ln Z - \xi}{\omega}\right)^2
        \right\}
        }
  %  }_{(1)} 
    \end{equation}
and (b) is the new term that allows for asymmetry, which is equal to the cumulative of the log-normal distribution, $\Phi$,
    \begin{equation}
    \begin{array}{cc}
 \Phi\left(\alpha \frac{\ln Z - \xi}{\omega} \right) &\equiv 
    \frac{1}{2} 
    \left[ 
        1 + {\rm erf}
            \left\{
                \alpha \frac{\ln Z - \xi}{\omega \sqrt{2}}
            \right\} 
    \right] \\
    \end{array}
\end{equation}

%
\noindent This introduces three parameters, $\alpha, \omega$ and $\xi$, each of which may depend on redshift. The first parameter, $\alpha$, is known as the ``shape''. It affects the skewness of the distribution and thus allows for asymmetries between metallicities that are higher and lower than the mean.  The symmetric log-normal distribution is recovered for $\alpha=0$. The second parameter, $\omega$  is known as the ``scale''. It provides a measure of the spread in metallicities at each redshift.   Finally, $\xi$, is known as the ``location'', because this parameter plays a role in setting the mean of the distribution at each redshift.

@@

We will also allow the ``scale'' $\omega$ to evolve with redshift in a similar manner, 
\begin{equation}
\label{eq: omega z}
    \omega(z) = \omega_0 \cdot 10^{\omega_z \cdot z}.
\end{equation}
where $\omega_0$ is
%$\omega_0 = 1.125$, 
the width of the metallicity distribution at $z=0$, and $\omega_z$
%$\omega_z = 0.048$, 
the redshift evolution of the scale.

@@

\paragraph{Asymmetry of the metallicity distribution: $\alpha$}
The skewness $\alpha$ could in principle also be allowed to evolve with redshift (e.g., $\alpha (z) = \alpha(z=0) 10^{\alpha_z \cdot z}$). 
However, we find no significant improvement over the simpler assumption where alpha is kept constant. 
Note that the redshift evolution of the `scale' (eq. \ref{eq: omega z}), already captures similar behaviour in our current formalism. We therefore adopt $ \alpha = \alpha(z=0)$ and $\alpha_z = 0$.

@@

\noindent where $\xi(z)$ and $\omega(z)$ are defined in Equations~\ref{eq mu z} and \ref{eq: omega z} respectively and we have assumed $\alpha$ to be constant.

%, and our fit value for $\alpha = -1.77$. Our set of parameters for \dpdZ is thus:  $\mu_0 = 0.025, \mu_z = -0.048, \omega_0 = 1.125, \omega_z = 0.048$ and $\alpha = -1.77$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Illustris-TNG Cosmological simulations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Both the large observational uncertainties in \SFRDzZ (as discussed in section \ref{sec: intro}), and the many uncertainties in cosmological simulations (as discussed below) call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work. Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.

The IllustrisTNG-project \citep[or TNG in short,][]{FirstResTNG_Springel2018,FirstResTNG_Marinacci2018, FirstResTNG_Nelson2018,FirstResTNG_Pillepich2018, FirstResTNG_Naiman2018} considers galaxy formation and evolution through large-scale cosmological hydrodynamical simulations.
Such simulations provide the tools to study parts of the Universe that are not easily accessible by observations. In particular of interest for this work, they simulate the high redshift enrichment of galaxies and the tail of low metallicity star formation at low redshift.
% Different cosmological simulations produce varying \SFRDzZ, depending on the adopted assumptions about the creation and distribution of metals.

The models implemented in the publicly available TNG simulations\footnote{ \url{https://www.tng-project.org/}} have lead to many successes. For a more extended discussion focused on the processes that govern the creation, distribution and mixing of metals in in the TNG simulations we refer to \cite{Pakmor+2022}. In short, star formation in the TNG simulations is calibrated against the Kennicutt–Schmidt relation \citep[][]{Schmidt1959,Kennicutt1989}. The stellar metallicity yields are an updated version of the original Illustris simulations as described in \cite{Pillepich2018}. Star particles deposit metals into the gas through type Ia and type II supernovae, as well as through asymptotic giant branch stars. 
% Positives on TNG
The TNG simulations have been shown to match observational constraints on the mass-metallicity relation of galaxies up to $z = 2$ \citep{Torrey+2019}, as well as iron abundances \citep{FirstResTNG_Naiman2018} and the metallicity gradients within galaxies at low redshift \citep{Hemler+2021}. %They reproduce the evolution of the sizes of galaxies with redshift \citep{Genel+2018}   
Several studies have used the TNG simulations to make predictions for astronomical transient sources \citep[e.g.][]{Briel+2021,Bavera+2022,vanson+2022}. In particular, \cite{Briel+2021} show that the \SFRDzZ from the TNG and the EAGLE \citep{Schaye+2015,Crain+2015} simulations provide the best agreement between observed and predicted cosmic rates for electromagnetic and gravitational-wave transients.

% Downsides of TNG100 
On the other hand, large uncertainties and crude approximations remain in all contemporary cosmological simulations, thus also in the TNG simulations. For example, dust is not included in the TNG simulations, which could mean that metallicity of the star-forming gas is overestimated. Furthermore, all stellar winds mass loss from massive stars, binary interactions and their ionising effects are ignored \citep[e.g.][]{Dray+2003,Smith2014,Gotberg+2020,DoughtyFinlator2021,Farmer2021_carbonfootprint,Goswami+2022}.
% pair-pulsational supernovae \citep[e.g.][]{Renzo+2020} .  
Moreover, the uniform ionising UV background is turned on abruptly at $z=6$, which crucially impacts the amount of low metallicity star formation at low redshift.

% These large uncertainties call for a generalised form of the \SFRDzZ that can be easily updated when new information becomes available, which is the motivation for this work. Although here, we only fit our model to the TNG100 simulation, our prescription can be easily be used to fit other simulated data or observational data of the metallicity dependent star formation rate density \footnote{We provide a Jupyter notebook to facilitate this fit here: \url{https://github.com/LiekeVanSon/SFRD_fit/blob/main/src/scripts/Fit_To_Cosmological_Simulation.ipynb} }.

@@

\begin{deluxetable*}{cll | cl}
\label{tab: fit params}
\tablecaption{Best fitting parameters for our \SFRDzZ fit to TNG100 data.}
\tablehead{\colhead{dP/dZ } & \colhead{description} & \colhead{best fit} & \colhead{SFRD(z)} & \colhead{best fit} } 
\startdata
$\mu_0$    & mean metallicity at $z=0$    & $0.025  \pm 0.001$ &  $a$ &  $0.02 \pm 0.05 \, \Msun\yr^{-1}\Mpc^{-3}$\\
$\mu_z$    & $z$-dependence of the mean   & $-0.048 \pm 0.001$ &  $b$ &  $1.48 \pm 0.01$\\
$\alpha$   & shape (skewness)             & $-1.767 \pm 0.05 $ &  $c$ &  $4.45 \pm 0.01$\\
$\omega_0$ & scale at $z=0$               & $1.125  \pm 0.005$ &  $d$ &  $5.90 \pm 0.02$\\
$\omega_z$ & $z$-dependence of the scale  & $0.048  \pm 0.0001$ &   \\
\enddata
\end{deluxetable*}

@@

Adopting a skewed-lognormal metallicity distribution allows for a tail of low metallicity star formation out to low redshifts. To emphasise the difference between a skewed-lognormal and a symmetric lognormal distribution, we show the phenomenological model from \cite{Neijssel+2019} in dotted grey. Their model falls within the family of functions that is encompassed by our model described in Section \ref{sec: model for sfrd(zZ)}, but we note that their model is distinctly different. \footnote{The phenomenological model from \cite{Neijssel+2019} is recovered by adopting $\mu_0= 0.035$, $\mu_z=-0.23$, $\omega_0=0.39 $, $\omega_z = 0$, $\alpha = 0$, $a=0.01$, $b=2.77$, $c=2.9$ and $d=4.7$. }
% The \SFRDzZ from \cite{Neijssel+2019} was optimised to match the local rate of double compact object mergers as presented in the second gravitational-wave catalogue. However, the resulting symmetric distribution cuts-off virtually all low-metallicity ($Z\leq 10^{-2.5}$) star formation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\script{SFR_z.py}
\includegraphics[width=0.47\textwidth]{figures/SFR_redshift.pdf}
\includegraphics[width=0.47\textwidth]{figures/SFR_tlookback.pdf}
\caption{Comparison of different \SFRDz
 \label{fig: SFR(z)}}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
